### 2019-09-25 liability.tex
updates management

\subsection{Dining}
University Catering, Round Barn, and the Garden Hotel in Urbana (soon to be the Radisson) assume all liability regarding foodborne illness derived from their respective events.

\subsubsection{Round Barn}
A $\$200$ non-refundable deposit is required for all functions to hold a room, and is due upon reservation. Security/damage deposits will be refunded 7 days after a scheduled event.

A finalized menu is required at least two weeks prior to the function. An accurate estimate of attendance must be submitted to the Round Barn seven days prior to an event.
Seventy-two hours prior to an event, the Round Barn must receive a final guaranteed attendance figure. This is what will be charged if the event falls under the final guaranteed attendance figure. If the final guaranteed attendance fall is under 90$\%$ of the previous seven-day estimate, the client will be charged for the difference at the rate of one-half the original per person rate.

Prices are subject to change without notice; however, pricing stated on a signed contract will be honored. Due to insurance regulations, it is forbidden to carry out any food or beverage provided by the Banquet Centre.

Cancellations of any function are required ninety days prior to the function or a penalty will be incurred.

>>>>

\subsection{Dining}
University Catering and the Garden Hotel in Urbana (soon to be the Radisson) assume all liability regarding foodborne illness derived from their respective events.

### 2019-09-25 main.tex
adds milestones
adds hotel info and jeremy bio
added socials
moves socials to program logistics
updates management and proglog
updates management

\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{eso-pic}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage{microtype} % Improves typography

\usepackage{fancyhdr}
% \usepackage{pagecounting}
% \usepackage[dvips]{color}

@@

\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\input{theme}
\newpage
\input{uiuc}
\newpage
\input{conflog}
\newpage
\input{proglog}
\newpage
\input{management}
\newpage
\input{budget}

>>>>

\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{eso-pic}
\usepackage{soul}
\usepackage{xcolor}
\usepackage[parfill]{parskip}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage{microtype} % Improves typography
\usepackage[toc,page]{appendix} % creates an appendix
\usepackage{fancyhdr}
% \usepackage{pagecounting}
% \usepackage[dvips]{color}

@@

\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
% \tikzstyle{arrow} = [thick,--,>=stealth]

@@

\input{theme}
\newpage
\input{uiuc}
\newpage
\input{conflog}
\newpage
\input{proglog}
\newpage
\input{management}
\newpage
\input{website}
\newpage
\input{budget}
\newpage
\input{liability}
\newpage
% Appendices
\appendix
\input{conflict}
\input{judging}
\input{schedule}
\input{building}
\input{locations}
\input{staffreq}
\input{facultyletter}
\input{petition}

### 2019-09-25 management.tex
updates management

% ===============================================
% This is the hierarchy breakdown
% ===============================================
\begin{center}
	\begin{tikzpicture}[
		chair/.style={rectangle, text centered, draw,fill=blue!20, execute at begin node={\begin{varwidth}{9em}},
   		execute at end node={\end{varwidth}}},
   		committee/.style={rectangle,draw,fill=green!40, text centered, execute at begin node={\begin{varwidth}{7em}},
   		execute at end node={\end{varwidth}}},
   		coordinator/.style={rectangle,draw,fill=red!30, text centered, execute at begin node={\begin{varwidth}{7em}},
   		execute at end node={\end{varwidth}}},
		grandchild/.style={grow=down,xshift=1em,anchor=west,
		edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}, execute at begin node={\begin{varwidth}{8em}},
   		execute at end node={\end{varwidth}}},
		first/.style={level distance=12ex},
		second/.style={level distance=24ex},
		third/.style={level distance=36ex},
		level 1/.style={sibling distance=11em}]
	    % Parents
	    \coordinate
	      child[grow=left] {node[chair,anchor=east]{General Co-Chair \\ (Sam Dotson)}}
	      child[grow=right] {node[chair,anchor=west]{Technical Co-Chair\\ (Jeremy Mettler)}}
	      child[grow=down,level distance=3ex]
	    [edge from parent fork down]
	    % Children and grandchildren
	    child{node[committee] {Non-Technical Subcommittee}
	      child[grandchild,first] {node[chair]{Logistics Chair}}
	      child[grandchild,second] {node[coordinator]{Hotels and Transportation}}
	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
	    child {node[committee] {Communications Subcommittee}
	      child[grandchild, first] {node[chair] {Publications Chair}}
	      child[grandchild, second] {node[coordinator]{Media}}
	      child[grandchild, third] {node[coordinator] {Program}}}
	    child{node[committee] {Financial Subcommittee}
	      child[grandchild,first] {node[chair]{Financial Chair}}
	      child[grandchild,second] {node[coordinator]{Registration}}
	      child[grandchild,third] {node[coordinator]{Sponsorship}}}
	    child {node[committee]{Technical Subcommittee}
	      child[grandchild,first] {node[chair]{Sessions Chair}}
	      child[grandchild,second] {node[coordinator]{Workshops}}
	      child[grandchild,third] {node[coordinator]{Career Fair}}};
	\end{tikzpicture}
\end{center}
% ===============================================
% ===============================================
% ===============================================

\subsection{Position Responsibilities}
The three co-chairs are responsible for setting up major milestones and 
ensuring that those milestones are met. Together they oversee all three subcommittees but 
are each primarily in charge of one. They will serve as the primary contacts between subcommittee
chairs and the faculty as well as professionals. The co-chairs have the final word on all 
conference decisions. They serve as the face of the conference and

\begin{itemize}
	\item $\large\textbf{\textit{General Co-Chair}}$\\
	In addition to the responsibilities outlined above, the General Co-Chair primarily oversees the
	Non-technical Subcommittee and the Media Coordinator. He works with the Technical Co-Chair to plan full committee
	meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
	Technical Subcommittee. Works with the General Co-Chair to plan full committee meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Financial Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Financial Co-Chair primarily oversees the Financial Subcommittee. The Financial Co-Chair is also responsible for interacting with businesses, the university, and ANS National for sponsorship needs. He completes any remaining tasks to ensure that milestones are met.

@@

		\item[$\circ$] $\textbf{Account Coordinator}$\\

>>>>

% ===============================================
% This is the hierarchy breakdown
% ===============================================
% \begin{center}
% 	\begin{tikzpicture}[
% 		chair/.style={rectangle, text centered, draw,fill=blue!20, execute at begin node={\begin{varwidth}{9em}},
%    		execute at end node={\end{varwidth}}},
%    		committee/.style={rectangle,draw,fill=green!40, text centered, execute at begin node={\begin{varwidth}{7em}},
%    		execute at end node={\end{varwidth}}},
%    		coordinator/.style={rectangle,draw,fill=red!30, text centered, execute at begin node={\begin{varwidth}{7em}},
%    		execute at end node={\end{varwidth}}},
% 		grandchild/.style={grow=down,xshift=1em,anchor=west,
% 		edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}, execute at begin node={\begin{varwidth}{8em}},
%    		execute at end node={\end{varwidth}}},
% 		first/.style={level distance=12ex},
% 		second/.style={level distance=24ex},
% 		third/.style={level distance=36ex},
% 		level 1/.style={sibling distance=11em}]
% 	    % Parents
% 	    \coordinate
% 	      child[grow=left] {node[chair,anchor=east]{General Co-Chair \\ (Sam Dotson)}}
% 	      child[grow=right] {node[chair,anchor=west]{Technical Co-Chair\\ (Jeremy Mettler)}}
% 	      child[grow=down,level distance=3ex]
% 	    [edge from parent fork down]
% 	    % Children and grandchildren
% 	    child{node[committee] {Non-Technical Subcommittee}
% 	      child[grandchild,first] {node[chair]{Logistics Chair}}
% 	      child[grandchild,second] {node[coordinator]{Hotels and Transportation}}
% 	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
% 	    child {node[committee] {Communications Subcommittee}
% 	      child[grandchild, first] {node[chair] {Publications Chair}}
% 	      child[grandchild, second] {node[coordinator]{Media}}
% 	      child[grandchild, third] {node[coordinator] {Program}}}
% 	    child{node[committee] {Financial Subcommittee}
% 	      child[grandchild,first] {node[chair]{Financial Chair}}
% 	      child[grandchild,second] {node[coordinator]{Registration}}
% 	      child[grandchild,third] {node[coordinator]{Sponsorship}}}
% 	    child {node[committee]{Technical Subcommittee}
% 	      child[grandchild,first] {node[chair]{Sessions Chair}}
% 	      child[grandchild,second] {node[coordinator]{Workshops}}
% 	      child[grandchild,third] {node[coordinator]{Career Fair}}};
% 	\end{tikzpicture}
% \end{center}
\begin{center}
	\begin{tikzpicture}
		\node (gen chair) [chair] {General Co-Chair (Sam Dotson)};
		\node (tech chair) [chair, right of = gen chair, xshift = 5cm] {Technical Co-Chair (Jeremy Mettler)};
		\node (div chair) [chair, left of = gen chair, xshift = -5cm] {Diversity Co-Chair (Nate Reid)};

		\node (log chair) [director, below of = gen chair, xshift = -2.5cm, yshift = -2cm] {Logistics Chair (Natalie Gaughan)};
		\node (med coord) [coordinator, below of = gen chair, xshift = 1cm, yshift = -4cm] {Media Coordinator (Nathan Ryan)};
		\node (prog coord) [coordinator, below of = log chair, yshift = -2cm] {Program Coordinator (Dilan K.)};
		\node (hat coord) [coordinator, below of = prog coord, yshift = -2cm] {Hotels and Transport (Gavin Davis)};
		\node (hoa coord) [coordinator, below of = hat coord, yshift = -2cm] {Hospitality and Accomodations (Brady Moran)};
		\node (tours coord) [coordinator, below of = hoa coord, yshift = -2cm] {Tours Coordinator (Anna Balla)};

		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwen Chee)};
		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator (Roberto Fairhurst)};
		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Zach Jeckell)};
		\node (cf coord) [coordinator, below of = sesh coord, yshift = -2cm] {Career Fair Coordinator (Greg Golba)};

		\node (fin chair) [director, below of = tech chair, xshift = -2cm, yshift = -2cm] {Financial Chair (Jack Stahl)};
		\node (spon coord) [coordinator, below of = fin chair, yshift = -2cm] {Sponsorships Coordinator (Jimmy Shehee)};
		\node (reg coord) [coordinator, below of = spon coord, yshift = -2cm] {Registration Coordinator (Jasmine Dinari)};

		\draw  (gen chair) -- (tech chair);
		\draw  (gen chair) -- (div chair);
		\draw  (gen chair) -- (log chair);
		\draw  (log chair) -- (prog coord);
		\draw  (prog coord) -- (hat coord);
		\draw  (hat coord) -- (hoa coord);
		\draw  (hoa coord) -- (tours coord);
		\draw  (gen chair) -- (med coord);
		\draw  (tech chair) -- (fin chair);
		\draw  (gen chair) -- (fin chair);
		\draw  (tech chair) -- (tsc chair);
		\draw  (fin chair) -- (spon coord);
		\draw  (spon coord) -- (reg coord);
		\draw  (tsc chair) -- (work coord);
		\draw  (work coord) -- (sesh coord);
		\draw  (sesh coord) -- (cf coord);
		\draw  (div chair) -- (log chair);

	\end{tikzpicture}
\end{center}

% ===============================================
% ===============================================
% ===============================================

\subsection{Position Responsibilities}
The three co-chairs are responsible for setting up major milestones and 
ensuring that those milestones are met. Together they oversee all three subcommittees. They will serve as the primary contacts between subcommittee chairs and the faculty as well as professionals. The co-chairs have the final word on all conference decisions. They serve as the faces of the conference.

\begin{itemize}
	\item $\large\textbf{\textit{General Co-Chair}}$\\
	In addition to the responsibilities outlined above, the General Co-Chair primarily oversees the
	Non-technical Subcommittee and the Media Coordinator. He works with the Technical Co-Chair to plan full committee
	meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
	Technical Subcommittee. Works with the General Co-Chair to plan full committee meetings and completes any remaining tasks to ensure that milestones are met.
	\item $\large\textbf{\textit{Diversity Co-Chair}}$\\
	In addition to the responsibilities outlined above, the Financial Co-Chair primarily oversees the Financial Subcommittee. The Financial Co-Chair is also responsible for interacting with businesses, the university, and ANS National for sponsorship needs. He completes any remaining tasks to ensure that milestones are met.

@@

		\item[$\circ$] $\textbf{Financial Chair}$\\
